How is experience transformed into memory?

### 2018-08-29 paper/main.tex
updated figure, updated legend, new supp methods section

In order to ascertain which features were important in relating the recall models to the video model, we similarly compared to the temporal structures of video and recall models deprived of a single feature at a time (Supp. Fig.~\ref{fig:feature-importance}B). For each feature removed, we transformed each participant’s recall transcript using a model trained on the feature-deprived video text windows (of 50 scene segments), and resampled the recall timeseries to match the shape of the video model (1976 timepoints). We then represented the temporal structures of each participant’s recall model as timepoints-by -timepoints correlation matrices and computed the average correlation with the temporal structure of the video model (across participants).

>>>>

In order to ascertain which features were important in relating the recall models to the video model, we similarly compared to the temporal structures of video and recall models deprived of a single feature at a time (Supp. Fig.~\ref{fig:feature-importance}B). For each feature removed, we transformed each participant’s recall transcript using a model trained on the feature-deprived video text windows (of 50 scene segments), and resampled the recall timeseries to match the shape of the video model (1976 timepoints). We then represented the temporal structures of each participant’s recall model as timepoints-by-timepoints correlation matrices and computed the average correlation with the temporal structure of the video model (across participants).

The two prior analyses examine information (about either the video model structure or the video/recall model relationship) lost in the absence of each feature. However, they do not consider redundancy in the information each feature contributes (e.g., how much unique information does "Character speaking" provide that "Character in focus" does not?). As a measure of information overlap between features, we computed the similarity between the topic trajectories of each individual annotated feature in addition to the full feature set. First, we singularly transformed the text of each feature using a model trained on the collection of all features. We then represented the single feature's model's temporal structure as a timepoints-by-timepoints correlation matrix, and compared the temporal structures pairwise by constructing a features-by-features correlation matrix ((Supp. Fig.~\ref{fig:feature-importance}C). We additionally computed the correlation between the individual features' temporal structures and that of the full video model as a measure of the proportion of information discernible from that feature alone.
